Update on simulation results and queries

### 2021-01-04 results_simulation.Rmd
adding norm  wpd for other non-standard normal distribution

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")

>>>>

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N01.png")
```

```{r normal05-norm, fig.cap="Density plots of normalised wpd is shown for Normal(0,5) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N05.png")
```

```{r normal51-norm, fig.cap="Density plots of normalised wpd is shown for Normal(5,1) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N51.png")
```

```{r normal55-norm, fig.cap="Density plots of normalised wpd is shown for Normal(5,5) distribution. The mean and sd of the distribution looks almost similar for different facet and x-axis categories.", fig.pos="h"}

knitr::include_graphics("simulations/norm/null_design_quantrans_nperm/figs/nxbyfacet_density_wpd_N55.png")
```
